{{< var titll >}}

### 2024-07-13 presentation.qmd
publishloss

>>>>

## {{< var sec2.un1 >}}

- Specify a loss function
  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
- $M(,)=$x+y$
  - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
  - Also: Euler rotation
- System approach Demands mulitvariate Manifold Equations
  - Univariate manifold Equation
  - Multivariate Manifold Equations
- Constrain on implementation
  - Flipping votes on one mode
  - Vote registration until upper limit

![](images/loss_5_conditions.png){width=300}
